R for Clinical Study Reports and Submission

### 2021-11-05 tlf-efficacy.Rmd
Apply suggestions from code review
Co-authored-by: yilong zhang <elong0527@gmail.com>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
primary and secondary efficacy endpoints need to summarized
in Section 11.4, Efficacy Results and Tabulations of Individual Participant.

>>>>

Following [ICH E3 guidance](https://database.ich.org/sites/default/files/E3_Guideline.pdf),
primary and secondary efficacy endpoints need to be summarized
in Section 11.4, Efficacy Results and Tabulations of Individual Participant.
